### 2023-07-31 paper/sec-dis-pseudodata.tex
Update event rates plot
Updating all xFitter plots in paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.6\textwidth]{plots/KIN_DIS_FPF.pdf}
    \caption{The kinematic coverage in the $(x,Q^2)$ plane
      of muon neutrino scattering
      at FASER$\nu$2, FLArE,
      and AdvSND (see also Fig.~\ref{fig:fasernu2_muon})
      compared to that of electron-ion collisions
      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
      as well as to the coverage of other available hard-scattering datasets involving
      nuclear targets or projectiles.
      %
      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
      production in proton-lead collisions at the LHC.
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
    \centering
    \includegraphics[width = 0.95\textwidth]{plots/error_plot_FASERv2_14.pdf}
    \caption{Same as Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
      %
      In addition to the event yield values, we also show the error bars corresponding to
      statistical errors only (left), systematic errors only (middle), and the
      sum in quadrature of the two (right panel).
      %
      The error bars in the horizontal direction indicate the width of the adopted $x$-bins.
      }
    \label{fig:error_plot_FASERv2_14}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The end result of the procedure is the estimate of statistical and systematic uncertainties
for each bin of the measurement, from which a experimental covariance matrix can be constructed as
\be
\label{eq:covmat_definition}
   {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
   + \sum_{k=1}^{n_{\rm sys}}\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp \lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(j)} \rp
   \, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
 \ee
  and the same for the associated correlation
 matrix of the measurement
 \be
 \rho_{ij} =  \frac{{\rm cov}_{ij}}{\sqrt{ {\rm cov}_{ii} }\sqrt{ {\rm cov}_{jj} } } \, . 
 \ee
 The relative covariance matrix, $ {\rm cov}_{ij}/( N_{\rm ev}^{(i)}N_{\rm ev}^{(j)})$, is
 independent of the considered observable and would also apply
 for the double-differential cross-sections Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) which are related to the event yields by a constant prefactor.
 %

@@

 The central values for the pseudo-data, denoted
 by $\mathcal{O}_i^{{\rm (exp)}} $, are obtained
 by fluctuating the reference theory prediction Eq.~(\ref{eq:theory_dis_projections})
 by the corresponding statistical and systematic
 uncertainties,
 \begin{equation}
  \label{eq:pseudo_data_v2}
  \mathcal{O}_i^{{\rm (exp)}}
  = \mathcal{O}_i^{{\rm (th)}}
    \left( 1+ r_i \delta_i^{\rm tot}
    \right) \,
    , \qquad i=1,\ldots,N_{\rm bin} \, ,
 \end{equation}
 where the total experimental uncertainty is the sum in quadrature of
 statistical and systematic errors, accounting for a possible reduction
 factor in the latter,
  \be
 \delta_{i}^{\rm tot}
 = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
 \left( f_{\rm red}^{(k)} \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, ,
 \qquad i=1,\ldots,N_{\rm bin} \, ,
 \ee
 and with $r_{i}$ being univariate Gaussian random numbers.
 %
 The pseudo-data generated by means of Eq.~(\ref{eq:pseudo_data_v2}),
 together with the corresponding covariance matrix
  \be
\label{eq:covmat_definition_v2}
 {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)} \mathcal{O}_i^{\rm (th)} \rp^2
 + \delta_{ij}\sum_{k=1}^{n_{\rm sys}}
 \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} \mathcal{O}_i^{\rm (th)} \rp^2
\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
\ee
define then the inputs of the subsequent proton and nuclear PDF determination.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.7\textwidth]{plots/KIN_DIS_FPF.pdf}
    \caption{The kinematic coverage in the $(x,Q^2)$ plane
      of muon neutrino scattering
      at FASER$\nu$2, FLArE,
      and AdvSND (see also Fig.~\ref{fig:fasernu2_muon})
      compared to that of electron-ion collisions
      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
      as well as to the coverage of other available hard-scattering datasets involving
      nuclear targets or projectiles.
      %
      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
      production in proton-lead collisions at the LHC.
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
    \centering
    \includegraphics[width = \textwidth]{plots/Event_Rate_FASERv2_antineutrino.pdf}
    \caption{Same as Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
      %
      In addition to the event yield values, we also show the error bars corresponding to
      statistical errors only (left), systematic errors only (middle), and the
      sum in quadrature of the two (right panel).
      %
      The error bars in the horizontal direction indicate the width of the adopted $x$-bins.
      }
    \label{fig:error_plot_FASERv2_14}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The end result of the procedure is the estimate of statistical and systematic uncertainties
for each bin of the measurement, from which a experimental covariance matrix can be constructed as
\be
\label{eq:covmat_definition}
   {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
   + \sum_{k=1}^{n_{\rm sys}}\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp \lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(j)} \rp
   \, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
 \ee
  and the same for the associated correlation
 matrix of the measurement
 \be
\label{eq:corrmat_definition}
 \rho_{ij} =  \frac{{\rm cov}_{ij}}{\sqrt{ {\rm cov}_{ii} }\sqrt{ {\rm cov}_{jj} } } \, . 
 \ee
 The relative covariance matrix, $ {\rm cov}_{ij}/( N_{\rm ev}^{(i)}N_{\rm ev}^{(j)})$, is
 independent of the considered observable and would also apply
 for the double-differential cross-sections Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) which are related to the event yields by a constant prefactor.
 %

@@

 The central values for the pseudo-data, denoted
 by $\mathcal{O}_i^{{\rm (exp)}} $, are obtained
 by fluctuating the reference theory prediction Eq.~(\ref{eq:theory_dis_projections})
 by the corresponding statistical and systematic
 uncertainties,
 \begin{equation}
  \label{eq:pseudo_data_v2}
  \mathcal{O}_i^{{\rm (exp)}}
  = \mathcal{O}_i^{{\rm (th)}}
    \left( 1+ r_i \delta_i^{\rm tot}
    \right) \,
    , \qquad i=1,\ldots,N_{\rm bin} \, ,
 \end{equation}
 where the total experimental uncertainty is the sum in quadrature of
 statistical and systematic errors, accounting for a possible reduction
 factor in the latter,
  \be
 \delta_{i}^{\rm tot}
 = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
 \left( f_{\rm red}^{(k)} \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, ,
 \qquad i=1,\ldots,N_{\rm bin} \, ,
 \ee
 and with $r_{i}$ being univariate Gaussian random numbers.
 %
 The pseudo-data generated by means of Eq.~(\ref{eq:pseudo_data_v2}),
 together with the corresponding correlations, computed according to Eq.s~\eqref{eq:corrmat_definition}--\eqref{eq:covmat_definition_v2},
%  \be
%\label{eq:covmat_definition_v2}
% {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)} \mathcal{O}_i^{\rm (th)} \rp^2
% + \delta_{ij}\sum_{k=1}^{n_{\rm sys}}
% \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} \mathcal{O}_i^{\rm (th)} \rp^2
%\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
%\ee
define then the inputs of the subsequent proton and nuclear PDF determination.

### 2023-07-31 paper/sec-protonPDFs.tex
Updating all xFitter plots in paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of FASER$\nu$2 structure functions
once charm-tagged measurements are removed.
%
In both cases, the covariance matrix accounts for systematic uncertainties.
}
\label{fig:profiling_charm}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
Fig.~\ref{fig:profiling_nochargediscrimination} compares the baseline LHC neutrino dataset with the results
of a profiling without allowing for the possibility of outgoing lepton charge separation.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{
Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of that being unable to identify
the charge of the outgoing lepton would have on the FASER$\nu$2 reach on the proton PDFs.
%
In both cases, the covariance matrix accounts for systematic uncertainties.
}
\label{fig:profiling_nochargediscrimination}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\bf add discussion of experiment sensitivity}
%
Same as Fig.~\ref{fig:profiling_syst} comparing FASER$\nu$2 with AdvSND and with FASER$\nu$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of FASER$\nu$2 structure functions
once charm-tagged measurements are removed.
}
\label{fig:profiling_charm}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
Fig.~\ref{fig:profiling_nochargediscrimination} compares the baseline LHC neutrino dataset with the results
of a profiling without allowing for the possibility of outgoing lepton charge separation.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{
Assessing the impact that being unable to identify
the charge of the outgoing lepton would have on the FASER$\nu$2 reach on the proton PDFs.
}
\label{fig:profiling_nochargediscrimination}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
Fig.~\ref{fig:profiling_experiment_comparison} shows a comparison of the impact 
that FASER$\nu$2 and FASER$\nu$ pseudodata have in PDF profiling, illustrating 
the improvement in precision obtainable with FASER$\nu$2.

\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/experiment_comparison/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
\caption{
A comparison of the effect of FASER$\nu$ and FASER$\nu2$ pseudodata in profiling, 
assuming only statistical uncertainties in the case of both experiments.
}
\label{fig:profiling_experiment_comparison}
\end{figure}
